Delocalization of Eigenvectors in Random Matrices

### 2025-03-24 Draft.tex
up to net ar

@@

\draw[thick, double] (a) -- (x);
\draw[blue, ->] (x) to (u);
\draw[wavy] (u) -- (v);
\draw[blue, ->] (u) -- (y);
\draw[thick, double] (y) -- (b);
\draw[red, ->] (x) to[bend right=47	] (y);
\draw[blue, ->] (v) to[out=200, in=150, loop] (v);
\end{tikzpicture}
$$\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_s(z)}_{xy} G_s(z)_{xu} S_{uv} 
\left[ G_s(z)_{vv} - m(z) \right] G_s(z)_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax} 
$$
\end{center}
By applying the loop expansion at edge $v$, we get the following four subgraphs: 
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (u) at (4, 0) {u};
\node (v) at (4, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};

@@

\end{tikzpicture}
$\lesssim  (t-s) W^{\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_t^{-3/2}\eta_s^{1/4} + W^{\delta_\sto/20}W^{-1/2}\eta_t^{-1}\eta_s^{3/4}\lesssim$
\end{center}
\begin{equation*}\lesssim W^{\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_t^{-3/2}\eta_s^{5/4} + W^{\delta_\sto/20}W^{-1/2}\eta_t^{-1}\eta_s^{3/4}\tag{6.1}\end{equation*}
This means that if we combine the diagram bound with the result above, we get: 
\begin{equation*}\max_{i=1, 2, 3, 4}|\mathcal{G}_{i0, s}|\lesssim W^{\delta_\sto/5}W^{-2+2\epsilon}\eta_t^{-3/2} + W^{\delta_\sto/5}W^{-2+2\epsilon}\eta_t^{-1}\eta_s^{1/2}\end{equation*}
Lastly, we need to integrate over $s\in [0, t]$ by using a change of variable $\sigma =\eta_s$, s.t. the bounds of the integral are $\sigma\in [\eta_t, \eta_0]$:
$$\max_{i=1, 2, 3, 4} \int_0^{t\wedge \tau_\sto}|\mathcal{G}_{i0, s}|ds\lesssim W^{\frac{\delta_\sto}{5}+2\epsilon} W^{-2}\eta_t^{-3/2} \int_{\eta_t}^{\eta_0}d\sigma + W^{\frac{\delta_\sto}{5}+2\epsilon}W^{-2}\eta_t^{-1}\int_{\eta_t}^{\eta_0}\sigma^{-1/2}d\sigma $$
\begin{equation*}\max_{i=1, 2, 3, 4} \int_0^{t\wedge \tau_\sto}|\mathcal{G}_{i0, s}|ds\lesssim W^{\frac{\delta_\sto}{5}+2\epsilon} W^{-2}\eta_t^{-\frac{3}{2}}\tag{6.2}\end{equation*}

\subsubsection*{Size estimates for $\mathcal{G}_{11, s}$}
In order to represent $B_{u\gamma} S_{\gamma\delta} G_{x_i\gamma}(G_{\delta\delta}-m)G_{\gamma y_i} f(G)$, we need to add the two new vertices $\gamma$ and $\delta$:
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (gamma) at (4, 0) {$\gamma$};
\node (u) at (4, 1) {u};
\node (v) at (5, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};
\node (delta) at (3, 1) {$\delta$};

@@

\end{tikzpicture}
\end{array}\right.$
\end{center}
Observe that the latter subgraphs are almost identical to the one we calculate for the $\mathcal{G}_{i0, s}$ estimates with the addition of a solid line. This means that we have to multiply our $(6.1)$ bound by an additional term $O(W^{\delta_\sto/20}W^{\frac{1}{2}+\epsilon}\eta_s^{-3/4})$ from estimate $(E1)$ to get a bound on the graph that is
$\lesssim W^{\delta_\sto/10}W^{2\epsilon}\eta_t^{-3/2}\eta_s^{\frac{1}{2}} + W^{\delta_\sto/10}W^{\epsilon}\eta_t^{-1}$
Multiplying this by $W^{\delta_\sto/5} W^{-2}\eta_s^{-1}$ results in the following bound:
$$\max_{i=1, \cdots, 4}| \mathcal{G}_{i1, s}|\lesssim W^{\frac{3\delta_\sto}{10}}W^{-2+2\epsilon}\eta_t^{-3/2}\eta_s^{-1/2}+W^{\frac{3\delta_\sto}{10}}W^{-2+\epsilon}\eta_t^{-1}\eta_s^{-1}$$
Following the same change of variables and integration, while also noting the fact that $\eta_0\lesssim 1$, gives us:
$$\Rightarrow \max_{i=1, \cdots, 4}\int_{0}^{t}|\mathcal{G}_{i1, a}|ds\lesssim W^{\frac{3\delta_\sto}{10}}W^{-2+2\epsilon}\eta_t^{-3/2}\int_{\eta_t}^{\eta_0}\sigma^{-1/2}d\sigma + W^{\frac{3\delta_\sto}{10}+\epsilon}W^{-2}\eta_t^{-1}\int_{\eta_t}^{\eta_0}\sigma^{-1}d\sigma\lesssim$$
$$\lesssim W^{\frac{3\delta_\sto}{10}}W^{-2+2\epsilon}\eta_t^{-3/2}\eta_0^{-1}-W^{\frac{3\delta_\sto}{10}}W^{-2+2\epsilon}\eta_t^{-1}+W^{\frac{3\delta_\sto}{10}+\epsilon}W^{-2}\eta_t^{-1}\ln \eta_0-W^{\frac{3\delta_\sto}{10}+\epsilon}W^{-2}\eta_t^{-1}\ln \eta_t$$
$$\lesssim W^{\delta'}W^{-2}\eta_t^{-3/2}\lesssim W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}},$$
since $\delta' = \frac{3\delta_\sto}{10}+2\epsilon>0$ is arbitrarily small. 
\subsubsection*{Size estimates for $\mathcal{G}_{12, s}$}
Following the regular vertex expansion, we have to now represent each of the subgraphs that has the form $\mathcal{G}_{i2, s}=B_{u\gamma} S_{\gamma \delta} G_{x_i\delta} (G_{\gamma\gamma}-m)G_{\delta y_i} f(G)$. By applying the graphical representation we get: 
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (delta) at (4, 0) {$\delta$};
\node (u) at (4, 1) {u};
\node (v) at (5, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};
\node (gamma) at (3, 1) {$\gamma$};

@@

\end{tikzpicture}. With this, we have verified that all the partial derivative terms satisfy the estimate $O(W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}})$. 
\subsubsection*{Combined bound}
How does Lemma 20 imply $\E^D_t$ is controlled?

>>>>

\begin{center}\label{graph}

@@

\draw[thick, double] (a) -- (x);
\draw[blue, ->] (x) to (u);
\draw[wavy] (u) -- (v);
\draw[blue, ->] (u) -- (y);
\draw[thick, double] (y) -- (b);
\draw[red, ->] (x) to[bend right=47	] (y);
\draw[blue, ->] (v) to[out=200, in=150, loop] (v);
\end{tikzpicture}
\begin{equation*}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}\overline{G_s(z)}_{xy} G_s(z)_{xu} S_{uv} 
\left[ G_s(z)_{vv} - m(z) \right] G_s(z)_{uy}\left[\{\text{Id} + (t-s)\Theta_t\}S^{1/2}\right]_{ax}  \tag{6}
\end{equation*}
\end{center}
By applying the loop expansion at edge $v$, we get the following four subgraphs: 
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (u) at (4, 0) {u};
\node (v) at (4, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};

@@

\end{tikzpicture}
$\lesssim  (t-s) W^{\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_t^{-3/2}\eta_s^{1/4} + W^{\delta_\sto/20}W^{-1/2}\eta_t^{-1}\eta_s^{3/4}\lesssim$
\end{center}
\begin{equation*}\lesssim W^{\delta_\sto/20}W^{-\frac{1}{2}+\epsilon}\eta_t^{-3/2}\eta_s^{5/4} + W^{\delta_\sto/20}W^{-1/2}\eta_t^{-1}\eta_s^{3/4}\tag{6.1}\end{equation*}
This means that if we combine the diagram bound with the result above, we get: 
\begin{equation*}\max_{i=1, 2, 3, 4}|\mathcal{G}_{i0, s}|\lesssim W^{\delta_\sto/5}W^{-2+2\epsilon}\eta_t^{-3/2} + W^{\delta_\sto/5}W^{-2+2\epsilon}\eta_t^{-1}\eta_s^{1/2}\end{equation*}
Lastly, we need to integrate over $s\in [0, t]$ by using a change of variable $\sigma =\eta_s$, s.t. the bounds of the integral are $\sigma\in [\eta_t, \eta_0]$:
$$\max_{i=1, 2, 3, 4} \int_0^{t\wedge \tau_\sto}|\mathcal{G}_{i0, s}|ds\lesssim W^{\frac{\delta_\sto}{5}+2\epsilon} W^{-2}\eta_t^{-3/2} \int_{\eta_t}^{\eta_0}d\sigma + W^{\frac{\delta_\sto}{5}+2\epsilon}W^{-2}\eta_t^{-1}\int_{\eta_t}^{\eta_0}\sigma^{-1/2}d\sigma $$
\begin{equation*}\max_{i=1, 2, 3, 4} \int_0^{t\wedge \tau_\sto}|\mathcal{G}_{i0, s}|ds\lesssim W^{\frac{\delta_\sto}{5}+2\epsilon} W^{-2}\eta_t^{-\frac{3}{2}}\lesssim W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}},\tag{6.2}\end{equation*}
since $\frac{\delta_\sto}{5}+2\epsilon$ is arbitrarily small. 
\newpage
\subsubsection*{Size estimates for $\mathcal{G}_{11, s}$}
In order to represent $B_{u\gamma} S_{\gamma\delta} G_{x_i\gamma}(G_{\delta\delta}-m)G_{\gamma y_i} f(G)$, we need to add the two new vertices $\gamma$ and $\delta$:
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (gamma) at (4, 0) {$\gamma$};
\node (u) at (4, 1) {u};
\node (v) at (5, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};
\node (delta) at (3, 1) {$\delta$};

@@

\end{tikzpicture}
\end{array}\right.$
\end{center}
Observe that the latter subgraphs are almost identical to the one we calculate for the $\mathcal{G}_{i0, s}$ estimates with the addition of a solid line. This means that we have to multiply our $(6.1)$ bound by an additional term $O(W^{\delta_\sto/20}W^{\frac{1}{2}+\epsilon}\eta_s^{-3/4})$ from estimate $(E1)$ to get a bound on the graph that is
$\lesssim W^{\delta_\sto/10}W^{2\epsilon}\eta_t^{-3/2}\eta_s^{\frac{1}{2}} + W^{\delta_\sto/10}W^{\epsilon}\eta_t^{-1}$
Multiplying this by $W^{\delta_\sto/5} W^{-2}\eta_s^{-1}$ results in the following bound:
$$\max_{i=1, \cdots, 4}| \mathcal{G}_{i1, s}|\lesssim W^{\frac{3\delta_\sto}{10}}W^{-2+2\epsilon}\eta_t^{-3/2}\eta_s^{-1/2}+W^{\frac{3\delta_\sto}{10}}W^{-2+\epsilon}\eta_t^{-1}\eta_s^{-1}$$
Following the same change of variables and integration, while also noting the fact that $\eta_0\lesssim 1$, gives us:
$$\Rightarrow \max_{i=1, \cdots, 4}\int_{0}^{t\wedge \tau_\sto}|\mathcal{G}_{i1, a}|ds\lesssim W^{\frac{3\delta_\sto}{10}}W^{-2+2\epsilon}\eta_t^{-3/2}\int_{\eta_t}^{\eta_0}\sigma^{-1/2}d\sigma + W^{\frac{3\delta_\sto}{10}+\epsilon}W^{-2}\eta_t^{-1}\int_{\eta_t}^{\eta_0}\sigma^{-1}d\sigma\lesssim$$
$$\lesssim W^{\frac{3\delta_\sto}{10}}W^{-2+2\epsilon}\eta_t^{-3/2}\eta_0^{-1}-W^{\frac{3\delta_\sto}{10}}W^{-2+2\epsilon}\eta_t^{-1}+W^{\frac{3\delta_\sto}{10}+\epsilon}W^{-2}\eta_t^{-1}\ln \eta_0-W^{\frac{3\delta_\sto}{10}+\epsilon}W^{-2}\eta_t^{-1}\ln \eta_t$$
$$\lesssim W^{\delta'}W^{-2}\eta_t^{-3/2}\lesssim W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}},$$
since $\delta' = \frac{3\delta_\sto}{10}+2\epsilon>0$ is arbitrarily small. 
\subsubsection*{Size estimates for $\mathcal{G}_{12, s}$}
Following the regular vertex expansion, we have to now represent each of the subgraphs that has the form $\mathcal{G}_{i2, s}=B_{u\gamma} S_{\gamma \delta} G_{x_i\delta} (G_{\gamma\gamma}-m)G_{\delta y_i} f(G)$. By applying the graphical representation we get: 
\begin{center}
\begin{tikzpicture}[
    thick, % Line thickness
    wavy/.style={decorate, decoration={snake, amplitude=2pt, segment length=5pt}},
    ]
\node (a) at (0,0) {a};
\node (x) at (2, 0) {x};
\node (delta) at (4, 0) {$\delta$};
\node (u) at (4, 1) {u};
\node (v) at (5, 1) {v};
\node (y) at (6, 0) {y};
\node (b) at (8, 0) {b};
\node (alpha) at (4, 2) {$\alpha$};
\node (beta) at (6, 2) {$\beta$};
\node (gamma) at (3, 1) {$\gamma$};

@@

\end{tikzpicture}. With this, we have verified that all the partial derivative terms satisfy the estimate $O(W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}})$. 
\subsubsection*{Combined bound}
All of the latter graph expansions allowed us to confirm the following result: $$\max_{a,b}\max_{i=1, \cdots, 4}\max_{j=0, 1, 2, 3} \left\vert \int_0^{t\wedge \tau_\sto}\mathcal{G}_{ij, s}(z)_{ab}ds\right\vert\lesssim W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$$
It is important to note that so far we have been working with the loop and regular vertex expansions without the regularization terms. Their bounds require more technical tools that work with isotropic bounds on graph modifications, and as such was outside the scope of this thesis. We simply state that the implication of their result (Lemma 22 \cite{bandSDE}) is within the stochastic bound we established above. As such, we can conclude that when we integrate the graph \hyperref[graph]{$(6)$} we started with over $s\in [0, t\wedge \tau_\sto]$ is $\prec W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$, given that all of the component terms in its sum expansion are of that order. Observe that everything we did applies WLOG to its conjguate, given that all of the bounds are the same. This in fact means that: $$\max_{a, b}\left\vert \int_0^{\tau_\sto\wedge t} \{\text{Id} + (t-s)\Theta_t\} S^{1/2}\Omega_s(z)S^{1/2} \{\text{Id} + (t-s)\Theta_t\}ds\right\vert \prec W^{-\frac{3}{4}}\eta_t^{-1}W^{-1}\eta_t^{-\frac{1}{2}}$$
\textcolor{red}{Hence, by a standard net argument}
